Supporting Information for [[main paper title]]

### 2021-03-01 SupportingInformation.Rmd
edits throughout

---
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
    number_sections: false
    keep_tex: true
    includes:
      in_header: "sipreamble.tex"
bibliography: "references.bib"
title: "Paper title"
author:
  - Author 1^[Institution 1, email1]
  - Author 2^[Institution 2, email2]
---

@@

>>>>

---
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
    number_sections: false
    keep_tex: true
    includes:
      in_header: "sipreamble.tex"
    extra_dependencies: ["float"]
bibliography: "references.bib"
title: "Supporting Information for [[main paper title]]"
author:
  - Aaron P. Ragsdale^[aaronpeaceragsdale@gmail.com]
date:
  - \today
---

@@

Yet to include:
- Tables with data presented in figures 5 and 6

## The diffusion equation, etc

\[ 
\frac{\partial \psi}{\partial t} = 
\frac{1}{2}\mathop{\sum\sum}_{1\leq i, j \leq 3} 
\frac{\partial^2}{\partial x_i \partial x_j} 
\left[\frac{x_i(\delta_{i=j}-x_j)\psi}{N(t)}\right] 
-\frac{\rho}{2}\left(\frac{\partial}{\partial x}\right) 
\]

## Moment equation and evolution operators

### Drift

### Recombination

### Mutation

### General selection

### Moment closure via jackknife approximation

## Data analysis

### Grouping Thousand Genomes populations based on clustering

Citation for Alex's work:
\url{https://www.abstractsonline.com/pp8/#!/9070/presentation/2384}

# Supplementary Tables

```{r selmodels, echo=F, tab.align="center"}
library(knitr)
library(kableExtra)
pops <- read.csv("tables/sel_models.txt", sep=";", header=TRUE, check.names=FALSE)
knitr::kable(pops, "latex", booktabs=T, escape=F,
    caption="General selection model for diploids and dominance models.") %>%
kable_styling(latex_options = "HOLD_position")
```

```{r epistasis, echo=F, tab.align="center"}
library(knitr)
library(kableExtra)
pops <- read.csv("tables/epistasis_model.txt", sep=";", header=TRUE, check.names=FALSE)
knitr::kable(pops, "latex", booktabs=T, escape=F,
    caption="Haploid epistasis model.") %>%
kable_styling(latex_options = "HOLD_position")
```

```{r 1kgpops, echo=F, tab.align="center"}
library(knitr)
library(kableExtra)
pops <- read.csv("tables/populations.txt", sep=";", header=TRUE, check.names=FALSE)
knitr::kable(pops, "latex", booktabs=T,
    caption="Thousand Genomes Project population descriptions for populations used in this study.") %>%
kable_styling(latex_options = "HOLD_position")
```

```{r tajimasD, echo=F, tab.align="center"}
library(knitr)
library(kableExtra)
taj <- read.csv("tables/tajimas_d.txt", sep=";", header=TRUE, check.names=FALSE)
knitr::kable(taj, "latex", booktabs=T, longtable=T,
    linesep = c("", "", "", "", "", "", "", "", "\\addlinespace"),
    caption="Tamija's $D$ for classes of coding mutations, both within annotated domains and outside of domains.") %>%
kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

# Supplementary Figures

1) Accuracy of jackknife for varying sample size
2) Repeat of figures 2, 3, and 4 but for average $D$ instead of $\sigma_d^2$
3)

```{r genespops, echo=F, fig.cap="(ref:figgenespopscap)", fig.align="center"}
knitr::include_graphics("figures/supp_gene_wide_all_pops.pdf")
```

(ref:figgenespopscap) **LD within and between protein-coding genes.** This is
the caption.

```{r domainspops, echo=F, fig.cap="(ref:figdomainspopscap)", fig.align="center"}
knitr::include_graphics("figures/supp_domain_all_pops.pdf")
```

(ref:figdomainspopscap) **LD within and between coding domains and pairs
outside domains at matched distances.** This is the caption.

```{r lddecay, echo=F, fig.cap="(ref:figlddecay)", fig.align="center"}
knitr::include_graphics("figures/supp_ld_decay.pdf")
```

(ref:figlddecay) **LD decay for synonymous and missense mutations for pairs
of mutations that fall outside of domains.**

```{r lddecaydomain, echo=F, fig.cap="(ref:figlddecaydomain)", fig.align="center"}
knitr::include_graphics("figures/supp_ld_decay_in_domain.pdf")
```

(ref:figlddecaydomain) **LD decay for synonymous and missense mutations for pairs
of mutations that fall inside the same domains.**
